Automated Verification Applied to Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-07-21 Tex/Old text/chapters/chapter04.tex
thesis updated text

\section{Intro to Automated Verification Experimental Evaluation}

Intro text here

-----------------------------------------
\section{Description of the Case Studies}
%------------------------------------------
%
%We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with peak power of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A). 
We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}. %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
\begin{table}
\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
\begin{scriptsize}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\hline
Item & House 1 & House 2 & House 3 & House 4 & House 5\\
\hline
\hline
PV Panels &  \multicolumn{4}{|c|}{3x 325 W: in series} & 4x 325 W: 2x series, 2x parallel \\
\hline
Batteries & \multicolumn{4}{|c|}{\makecell{4x220 Ah: 2x series, 2x parallel\\ autonomy: 48 h}} & \makecell{4x 120 Ah batteries in series\\ autonomy: 6 h}\\
\hline
Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150 V/35 A}\\
\hline
Inverter & \multicolumn{4}{|c|}{700 W, peak of 1,600 W} & 1,200 W, peak of 1,600 W\\
\hline
Power demand & 253 W & 263 W & 283 W & 501 W & 915 W\\
\hline
GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
\hline
Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
\hline
\hline
\end{tabular}
\end{scriptsize}
\end{table}
%------------------------------------------
\section{Objectives and Setup}
\label{sec:setup}
%------------------------------------------
Our experimental evaluation aims to answer two research questions:
%
\begin{enumerate}
\item[RQ1] \textbf{(soundness)} Does our automated verification approach provide correct results?
\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
\end{enumerate}

%In order to evaluate the proposed verification method and its performance, we have considered five case studies, three verification engines in different configurations, and also compared the results to the HOMER Pro tool. All the experiments were performed with a timeout of 14,400 seconds. %Every dweller, who owns a PV system, was interviewed 
%
All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. The setup of HOMER Pro v3.12.0: Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Windows 10. The experiments were performed with timeout of 14,400 seconds.

@@

% enabled with the goal of reducing memory usage; 
%The experiments were performed without a predefined timeout.
Verification engine CPAchecker 1.8 was used \footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, with the SMT solver MathSAT version 5.5.3~\cite{mathsat5}. An alternative CPAchecker configuration was tried as well, using BMC k-induction option, but without improvements of performance or soundness.
% enabled with the goal of reducing memory usage; 
 %The experiments were performed without a predefined timeout.

>>>>

This Chapter is devoted to the results of using automated verification to validate the intended behavior of stand-alone solar PV systems. Moreover, there is the comparative with a specialized simulation tool, and even the use of different verifiers who perform the automated verification in order to evaluate performance.

\section{Description of the Case Studies}
%------------------------------------------
%
%We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with peak power of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A). 
We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}. %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
These case studies were defined 
based on usual electrical load found in riverside communities of the 
Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.

\begin{table}
\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
\begin{scriptsize}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\hline
Item & House 1 & House 2 & House 3 & House 4 & House 5\\
\hline
\hline
PV Panels &  \multicolumn{4}{|c|}{3x 325 W: in series} & 4x 325 W: 2x series, 2x parallel \\
\hline
Batteries & \multicolumn{4}{|c|}{\makecell{4x220 Ah: 2x series, 2x parallel\\ autonomy: 48 h}} & \makecell{4x 120 Ah batteries in series\\ autonomy: 6 h}\\
\hline
Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150 V/35 A}\\
\hline
Inverter & \multicolumn{4}{|c|}{700 W, peak of 1,600 W} & 1,200 W, peak of 1,600 W\\
\hline
Power demand & 253 W & 263 W & 283 W & 501 W & 915 W\\
\hline
GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
\hline
Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
\hline
\hline
\end{tabular}
\end{scriptsize}
\end{table}

%------------------------------------------
\section{Objectives and Setup}
\label{sec:setup}
%------------------------------------------
Our experimental evaluation aims to answer two research questions:
%
\begin{enumerate}
\item[RQ1] \textbf{(soundness)} Does our automated verification approach provide correct results?
\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
\end{enumerate}

%In order to evaluate the proposed verification method and its performance, we have considered five case studies, three verification engines in different configurations, and also compared the results to the HOMER Pro tool. All the experiments were performed with a timeout of 14,400 seconds. %Every dweller, who owns a PV system, was interviewed 
%
All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. The setup of HOMER Pro v3.13.1 was an Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Windows 10. The experiments were performed with timeout of 240 minutes.

@@

% enabled with the goal of reducing memory usage; 
%The experiments were performed without a predefined timeout.
Verification engine CPAchecker 1.8 was used \footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, with the SMT solver MathSAT version 5.5.3~\cite{mathsat5}. An alternative CPAchecker configuration was tried as well, using BMC k-induction option, but without improvements of performance or soundness in the results (so it is not reported here).
% enabled with the goal of reducing memory usage; 
 %The experiments were performed without a predefined timeout.

\section{Verifiers Environment}
\label{sec:verifenviron}

Screens and comments about the verifiers.

\subsubsection{CBMC}

\subsubsection{ESBMC}

\subsubsection{CPAchecker}

\section{HOMER Pro Environment}
\label{sec:homerenviron}

Screens and comments about the simulation tool.

### 2019-07-21 Tex/Old text/chapters/chapter05.tex
thesis updated text

%\section{Intro to Automated Formal Synthesis Optimization}
This section presents the case studies used to evaluate our proposed approach. 
We also compare our approach with a simulation tool, named HOME Pro. 
The version and command-line of each verifier adopted, 
the computing setup, the objectives of the experimental phase, 
and the results itself are also described.

@@

All experiments regarding the verification tools were conducted 
on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
$2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
Related to HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores), 
with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
Our experiments were performed with a predefined timeout of $240$ minutes.

Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency. Note that ``incremental'' ESBMC with the SMT solver Z3 was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory. The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.

>>>>

%\section{Intro to Automated Formal Synthesis Optimization}
This Chapter presents the case studies used to evaluate the proposed approach of optimal sizing of stand-alone solar PV systems using automated synthesis. 
Moreover, the approach is compared with a simulation tool, named HOME Pro. 
The version and command-line of each verifier adopted, 
the computing setup, the objectives of the experimental phase, 
and the results itself are also described.

@@

All experiments regarding the verification tools were conducted 
on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
$2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
Related to HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores), 
with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
The experiments were performed with a predefined timeout of $240$ minutes.

Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} version 6.0.0 with solver Boolector 3.0.1~\cite{Brummayer}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engine to compare the proposed approach effectiveness and efficiency. Note that ``incremental'' ESBMC with the SMT solver Z3 version 4.7.1~\cite{DeMoura} was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory. The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
